Exploring the Impact of Encouragement and Student Behaviour on Academic Effort in Second-year Statistics Courses

### 2024-12-04 paper/paper.qmd
Update "paper"

The model estimates the relationship between these predictors and the response variable, change_effort, which quantifies how each factor contributes to the variations in student effort. By employing the `rstanarm` package [@rstanarm], the Bayesian approach accommodates uncertainty in the coefficients and provides posterior distributions for each parameter.

>>>>

The model estimates the relationship between these predictors and the response variable, change in effort, which quantifies how each factor contributes to the variations in student effort. By employing the `rstanarm` package [@rstanarm], the Bayesian approach accommodates uncertainty in the coefficients and provides posterior distributions for each parameter.
